\ttitle

### 2015-08-25 Chapters/Discussion.tex
Discussion - Everything is in the right place.

Reyad and co-workers performed a randomised trial of the effect of dobutamine infusion during pancreaticoduodenectomy on splanchnic perfusion, hemodynamics, and overall postoperative outcome \parencite{reyad_effect_2013}. 
They reported that intra-operative dobutamine use was associated with improved global oxygen delivery as measured by arterial and venous blood gases. 
Splanchnic perfusion as measured by gastric tonometry also improved.
It was interesting to note that the incidence of anastomotic leak was 30\% in the control group, 15\% in the group that received 3$\mu$g/kg/min of dobutamine and 5\% in the group that received 5$\mu$g/kg/min of dobutamine (p$<$0.05). 
The overall complication rate also decreased from 70\% in the control group to 40\% and 20\% in the dobutamine groups (p$<0.05$).

However, the benefit of goal-directed therapy to improve organ perfusion and oxygen delivery in improving postoperative outcomes remains unclear \parencite{grocott_perioperative_2013, pearse_effect_2014}. 
A recent randomised controlled trial evaluated the role of goal-directed therapy in high-risk patients undergoing major elective surgery that targeted individualised oxygen delivery \parencite{ackland_individualised_2015}.
The study did show that patients whose postoperative oxygen delivery was similar to their preoperative values had fewer complications.
However, oxygen delivery was not influenced by goal-directed therapy as any beneficial effect of the intervention was lost with the autonomic nervous system changes that accompanied the increased intravenous fluids and inotropes in the treatment cohort.

Improving oxygen delivery and organ perfusion in surgical patients remain the subjects of intense research.
However, the results presented in this thesis support the argument for therapeutic interventions aimed at improving oxygen delivery and organ perfusion before the patient with pancreatic cancer reaches the operating room as outlined in section \ref{disc_prehabilitation}.

@@

`Failure to rescue' after postoperative complications is one of the factors responsible for the discrepancy between morbidity and mortality in low-volume versus high-volume centres.
Mortality rates in patients undergoing a variety of complex surgical procedures including pancreatectomy was 2.5 times higher in low-volume centres than high-volume centres. 
However, complication rates were similar between these hospitals. 
Failure to identify and manage complications aggressively may have resulted in the increased mortality in the low-volume hospitals \parencite{ghaferi_complications_2009}.
In a recent large study involving nearly 2 million surgical patients, Ferraris VA and co-workers studied the outcome of over two-hundred thousand patients who had complications. 
They noted that 20\% of high-risk patients accounted for 90\% of deaths due to postoperative complications. 
They also reported that a simple risk-scoring system based on preoperative characteristics was able to identify these patients. 
Early recognition of complications in these patients and aggressive management may result in improved outcomes in these high risk patients.
These findings are supported by other studies involving emergency abdominal surgery \parencite{sheetz_improving_2013} and patients at major trauma centres \parencite{haas_prevention_2011}

>>>>

Reyad and co-workers performed a randomised trial of the effect of dobutamine infusion during pancreaticoduodenectomy on splanchnic perfusion, hemodynamics, and overall postoperative outcome \parencite{reyad_effect_2013}. 
They reported that intra-operative dobutamine use was associated with improved global oxygen delivery as measured by arterial and venous blood gases. 
Splanchnic perfusion measured by gastric tonometry also improved.
It was interesting to note that the incidence of anastomotic leak was 30\% in the control group, 15\% in the group that received 3$\mu$g/kg/min of dobutamine and 5\% in the group that received 5$\mu$g/kg/min of dobutamine (p$<$0.05). 
The overall complication rate also decreased from 70\% in the control group to 40\% and 20\% in the dobutamine groups (p$<0.05$).

However, the benefit of such goal-directed therapy to improve organ perfusion and oxygen delivery in improving postoperative outcomes remains unclear \parencite{grocott_perioperative_2013, pearse_effect_2014}. 
A recent randomised controlled trial evaluated the role of goal-directed therapy in high-risk patients undergoing major elective surgery that targeted individualised oxygen delivery \parencite{ackland_individualised_2015}.
The study did show that patients whose postoperative oxygen delivery was similar to their preoperative values had fewer complications.
However, oxygen delivery was not influenced by goal-directed therapy as any beneficial effect of the intervention was lost with the autonomic nervous system changes that accompanied the increased intravenous fluids and inotropes in the treatment cohort.

%Improving oxygen delivery and organ perfusion in surgical patients remain the subjects of intense research.
However, the results presented in this thesis support the argument for therapeutic interventions aimed at improving oxygen delivery and organ perfusion before the patient reaches the operating room as outlined in section \ref{disc_prehabilitation}.

@@

`Failure to rescue' after postoperative complications is one of the factors responsible for the discrepancy between morbidity and mortality in low-volume versus high-volume centres.
Mortality rates in patients undergoing a variety of complex surgical procedures including pancreatectomy was 2.5 times higher in low-volume centres than high-volume centres \parencite{ghaferi_complications_2009}.
However, complication rates were similar between these hospitals. 
Failure to identify and manage complications aggressively may have resulted in the increased mortality in the low-volume hospitals.
In a recent large study involving nearly 2 million surgical patients, Ferraris VA and co-workers studied the outcome of over two-hundred thousand patients who had complications \parencite{ferraris_va_identification_2014}. 
They noted that 20\% of high-risk patients accounted for 90\% of deaths due to postoperative complications. 
They also reported that a simple risk-score based on preoperative characteristics was able to identify these patients. 
Early recognition of complications in these high patients and aggressive management will reduce mortality.
These findings are supported by other studies involving emergency abdominal surgery \parencite{sheetz_improving_2013} and major trauma \parencite{haas_prevention_2011}
